### 2018-04-29 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Notes Update
Notes update

\end{axis}
\end{tikzpicture}
$$2\Bigg(\cos\Big(\frac{5\pi}{6}\Big)+i\sin\Big(\frac{5\pi}{6}\Big)\Bigg)$$
\subsection{$re^{i\theta}$}
This uses the same parameters as $r(\cos\theta+i\sin\theta)$

@@

$$32\cos^5\theta=\textcolor{red}{2\cos\theta}+\textcolor{Green}{10\cos3\theta}+\textcolor{Plum}{20\cos\theta}$$
$$\cos^5\theta=\frac{\cos\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$

@@

\end{axis}
\end{tikzpicture}
\section{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}
\end{document}

>>>>

\end{axis}
\end{tikzpicture}
\end{center}
$$2\Bigg(\cos\Big(\frac{5\pi}{6}\Big)+i\sin\Big(\frac{5\pi}{6}\Big)\Bigg)$$
\subsection{$re^{i\theta}$}
This uses the same parameters as $r(\cos\theta+i\sin\theta)$
\section{Absolute square}
When squaring $|z|$, where $z=x+iy$, first find $|z|$, which is $\sqrt{x^2+y^2}$, then square it to get $x^2+y^2$.

@@

$$32\cos^5\theta=\textcolor{red}{2\cos5\theta}+\textcolor{Green}{10\cos3\theta}+\textcolor{Plum}{20\cos\theta}$$
$$\cos^5\theta=\frac{\cos5\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$

@@

\end{axis}
\end{tikzpicture}
\section{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}
When doing translations, the input is $z=x+iy$ and the output is $w=u+iv$, unless otherwise stated.
\end{document}
